---
title: "Memory Archive"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
  gfm: default
execute:
  echo: false
  warning: false
---

## Overview

This is the rendered memory archive for the OpenClaw agent system.

## Directory Structure

| Tier | Path | Purpose |
|------|------|---------|
| CANON | `memory/10_CANON/` | Small, stable, curated |
| PROJECTS | `memory/20_PROJECTS/` | Bounded, scoped |
| SESSIONS | `memory/30_SESSIONS/` | Append-only daily notes |
| WORKING | `memory/40_WORKING/` | Inbox/scratch (emptied nightly) |

## Quick Links

- [Constraints](memory/10_CANON/constraints.md)
- [Preferences](memory/10_CANON/preferences.md)
- [Decisions](memory/10_CANON/decisions.md)
- [Today's Session](memory/30_SESSIONS/2026-02-27.md)

## Session Log

```{r}
#| echo: false
#| results: asis

# List all session files
session_files <- list.files("memory/30_SESSIONS", pattern = "\\.md$", full.names = TRUE)
if (length(session_files) > 0) {
  cat("### Recent Sessions\n\n")
  for (f in sort(session_files, decreasing = TRUE)) {
    cat(sprintf("- [%s](%s)\n", basename(f), f))
  }
}
```

## Model Configuration

**Primary Provider:** Groq  
**Default Model:** qwen/qwen3-32b  
**Fallback Chain:** See [routing-config.json](routing-config.json)

## Last Updated

```{r}
#| echo: false
Sys.time()
```